\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
typo
transformations

paragraph{Formal approach and semantics.}

@@

>>>>

\paragraph{Formal approach and semantics.}

@@

\subsection{Constraint Transformation}

Constraint of the type \emph{minimum qualified cardinality restriction (R-75)} expressed in OWL 2:

\begin{ex}[commandchars=\\\{\}]
Publication 
    a owl:Restriction ;
    owl:minQualifiedCardinality 1 ;
    owl:onProperty author ;
    owl:onClass Person .
\end{ex}

The same constraint expressed generically using the RDF-CV:

\begin{ex}[commandchars=\\\{\}]
[   a rdfcv:SimpleConstraint ;
    rdfcv:contextClass :Publication ;
    rdfcv:leftProperties ( :author ) ;
    rdfcv:classes ( :Person ) ;
    rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
    rdfcv:constrainingValue 1 ] .
\end{ex}

SPIN inference rule to infer the generic constraint:

\begin{ex}
rdfcv2spin:ToInfer 
	spin:rule [
		a sp:Construct ;
        	sp:text """
            	CONSTRUCT {            
                    :minimum-qualified-cardinality-restrictions
                        a rdfcv:SimpleConstraint ;
  				        rdfcv:contextClass ?this ;
  				        rdfcv:leftProperties :leftProperties ;
				        rdfcv:classes :classes ;
				        rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
				        rdfcv:constrainingValue ?cv .  
				    :leftProperties 
				        rdf:first ?lp1 ;
                        rdf:rest rdf:nil .    
                    :classes 
				        rdf:first ?c1 ;
                        rdf:rest rdf:nil .  
            	}
            	WHERE {
				    ?this
				        a owl:Restriction ;
				        owl:minQualifiedCardinality ?cv ;
				        owl:onProperty ?lp1 ;
				        owl:onClass ?c1 .         
        		} """ ; ] .
\end{ex}

The property \emph{spin:rule} can be used to link an rdfs:Class with SPARQL CONSTRUCT queries. Each query defines an inference rule that is applied to all instances of the associated class and its subclasses. The inference rule defines how additional triples can be inferred from what is stated in the WHERE clause. For each binding of the pattern in the WHERE clause of the rule, the triple templates from the CONSTRUCT clause are instantiated and added as inferred triples to the underlying model. At query execution time, the SPARQL variable ?this is bound to the current instance of the class.
